%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Senior Product Experience Designer III} % Job title
    {Dynatrace} % Organization
    {} % Location
    {Feb. 2023 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Led pattern governance for Strato, Dynatrace's enterprise design system, driving 90\% immediate adoption across 8 to 12 core development teams.}
        \item {Established GUIDE, a UX review framework to audit UI inconsistencies, accessibility gaps, and friction points across product surfaces at scale.}
        \item {Improved designer satisfaction scores by 43\% through high-leverage pattern documentation and actionable implementation references.}
        \item {Owned Figma component libraries end-to-end: complex components, data visualization, iconography, and library architecture.}
        \item {Prototyped and coded design proofs to validate implementation patterns and ensure cross-team technical compatibility.}
        \item {Facilitated pattern qualifier sessions and workshops to drive adoption, build contributor momentum, and align design and engineering teams.}
        \item {Advocated for design system value with non-design stakeholders, translating system decisions into business impact.}
        \item {Pioneered an internal AI agent initiative to enforce UI consistency at scale, defining the guidelines, constraints, and playbook that govern layout patterns, common actions, data ingestion flows, and permission priming across product surfaces. Adoption of agent-assisted workflows contributed directly to the 90\% pattern adoption rate across design and engineering teams.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Senior Design System Designer} % Job title
    {Stuart Delivery} % Organization
    {} % Location
    {Oct. 2021 - Nov. 2022} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Owned end-to-end Figma component libraries for a multi-platform design system spanning React, SwiftUI, and Flutter, maintaining full backward compatibility across all three.}
        \item {Identified resource constraints and proposed a federated collaboration model as the strategic solution, presenting directly to VP of Product, VP of Technology, and Director of Design to secure organizational buy-in.}
        \item {Established a Design System Champions program, distributing ownership across product teams to drive adoption and reduce dependency on a central team.}
        \item {Maintained Figma libraries as the single source of truth for design decisions, ensuring all components reflected the latest design standards regardless of engineering sync lag.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {UI Architect (Design Systems)} % Job title
    {FOSH Tech} % Organization
    {} % Location
    {Oct. 2020 - Apr. 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Embedded with distributed teams across Latin America, Europe, and North America to audit, modernize, and implement a unified design system under a single umbrella brand.}
        \item {Delivered 60\% faster feature implementation through reusable components and a scalable design token system covering color, typography, and sizing.}
        \item {Migrated 35+ components to modern architecture, achieving 40\% reduction in bundle size.}
        \item {Evaluated and selected Carbon Design System after building proof of concepts with Polaris, Pajamas, and Gestalt, choosing Carbon for its Svelte support and technical alignment.}
        \item {Led knowledge-sharing sessions across design, engineering, and marketing teams, distributing best practices so teams could contribute independently after engagement ended.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {UI Engineer (Design Systems)} % Job title
    {GIG} % Organization
    {} % Location
    {Feb. 2019 - Sep. 2020} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Built MagicWand, a white-label Vue.js UI kit serving 15+ regulated casino and sportsbook clients, reducing time-to-market from 6+ months to 60 days.}
        \item {Architected CSS Custom Properties theming system via Shadow DOM, enabling full brand isolation per client instance without CSS pollution or conflicts.}
        \item {Led 5+ major theme implementations and conducted theming workshops for design agencies and new engineering hires.}
        \item {Improved platform load performance by 40\% through Shadow DOM encapsulation and render optimization.}
      \end{cvitems}
    }

% %---------------------------------------------------------
%   \cventry
%     {Product Designer} % Job title
%     {Crucijuegos} % Organization
%     {} % Location
%     {Sep. 2017 - Jan. 2019} % Date(s)
%     {
%       \begin{cvitems} % Description(s) of tasks/responsibilities
%         \item {Led UX design for e-commerce platform, from research through prototyping.}
%         \item {Collaborated with engineering on front-end implementation.}
%       \end{cvitems}
%     }

% %---------------------------------------------------------
%   \cventry
%     {UI Developer} % Job title
%     {eCloud} % Organization
%     {} % Location
%     {2017} % Date(s)
%     {
%       \begin{cvitems} % Description(s) of tasks/responsibilities
%         \item {Developed pixel-perfect interfaces for Magento2, WordPress, and Shopify.}
%       \end{cvitems}
%     }

% %---------------------------------------------------------
%   \cventry
%     {UI Designer} % Job title
%     {Donweb} % Organization
%     {} % Location
%     {2016 - 2017} % Date(s)
%     {
%       \begin{cvitems} % Description(s) of tasks/responsibilities
%         \item {Created high-fidelity prototypes and CSS styling.}
%       \end{cvitems}
%     }

%---------------------------------------------------------
\end{cventries}