%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode

%-------------------------------------------------------------------------------
% CONFIGURATIONS
%-------------------------------------------------------------------------------
\documentclass[10pt, a4paper]{awesome-cv}

\geometry{left=1.4cm, top=.8cm, right=1.4cm, bottom=1.8cm, footskip=.5cm}

\colorlet{awesome}{awesome-red}
\setbool{acvSectionColorHighlight}{false}
\renewcommand{\acvHeaderSocialSep}{\quad\textbar\quad}

%-------------------------------------------------------------------------------
%	PERSONAL INFORMATION
%-------------------------------------------------------------------------------
\name{Iván}{Díaz Bonansea}
\position{Senior Product Experience Designer}
\address{}

\email{diazivanluis@gmail.com}
\homepage{http://ivncsdb.netlify.app/}
\linkedin{ivandb}

%-------------------------------------------------------------------------------
%	LETTER INFORMATION
%-------------------------------------------------------------------------------
\recipient
  {Netflix Recruiting Team}
  {Netflix\\Warsaw, Poland}
\letterdate{\today}
\lettertitle{Application for Design System Engineer --- Hawkins Professional}
\letteropening{Dear Netflix Team,}
\letterclosing{Sincerely,}
\letterenclosure[Attached]{Curriculum Vitae}

%-------------------------------------------------------------------------------
\begin{document}

\makecvheader[R]

\makecvfooter
  {\today}
  {Iván Díaz Bonansea~~~·~~~Cover Letter}
  {}

\makelettertitle

%-------------------------------------------------------------------------------
%	LETTER CONTENT
%-------------------------------------------------------------------------------
\begin{cvletter}

\lettersection{About Me}
I am a product designer and UI engineer with eight years of experience building
design systems across Europe. My background sits between design and engineering:
I write code to proof concepts, work hands-on with developers, and have led
systems from token architecture to pattern governance at scale. I care as much
about developer experience as I do about the design side.

\lettersection{Why Netflix?}
The Hawkins Professional role is exactly the kind of work I have been doing and
want to keep doing at a higher level of scale and complexity. Most recently at
Dynatrace I owned pattern governance across 60+ product teams, working at the
intersection of design and engineering to enforce consistency at scale. Part of
that work involved building an AI-assisted linting initiative: a structured
playbook that developers could run against their implementations automatically,
without waiting on human review. The parallels with what Hawkins is doing around
GenAI adoption and developer experience are not lost on me.

Before that I led Keirin, Stuart's cross-platform design system across React,
Flutter and SwiftUI, and built MagicWand at GIG --- a white-label Vue.js
component library powering 15+ client instances with Shadow DOM encapsulation
and a CSS custom properties theming API.

I am also genuinely excited about Warsaw. I have visited several times over the
years and have long-term friends who are locals. Relocating there feels like a
natural fit, not a compromise.

\lettersection{Why Me?}
What does not fit neatly into bullet points is this: I care about the work past
the deadline. I mentor willingly, communicate openly, and leave teams and systems
better than I found them. Building something that 1,600 engineers rely on daily
is exactly the kind of long-term, high-ownership challenge I am looking for, and
I would welcome the chance to discuss it further.

\end{cvletter}

\makeletterclosing

\end{document}